\Title

### 2021-02-15 manuscript/content.tex
Replace allocating for storing
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>

Worth noting that two sets of equivalent sources obtained through two adjacent
overlapping windows have some portion of the sources on the same locations,
specifically the ones that fall on the intersection between the two windows.
We can interpret this as the gradient-boosting algorithm fitting the source
coefficients multiple times: one time for every window that covers each source.
This fact can be exploited in order to save some computational memory.
Instead of allocating the multiple $\mathbf{c}_k$ vectors
(Eq.~\ref{eq:gb-linear-model}), we can initialize a single $\mathbf{c}$ vector
full of zeros, where each element represents the coefficient of each one of the
original $M$ sources.
After each iteration of the gradient-boosting algorithm, we add the product of
the resulting coefficients $\hat{\mathbf{c}}_k$ and the step-size coefficient
$\alpha_k$  to the $\mathbf{c}$ vector, respecting the order of its elements.
Because the relation between the source coefficients and the effect they
generate is linear, we can safely compute the resulting field through
Equation~\ref{eq:eql-forward}.
This way the memory needed to store the entire set of estimated coefficients is
limited to a single vector of $M$ elements.

>>>>

Worth noting that two sets of equivalent sources obtained through two adjacent
overlapping windows have some portion of the sources on the same locations,
specifically the ones that fall on the intersection between the two windows.
We can interpret this as the gradient-boosting algorithm fitting the source
coefficients multiple times: one time for every window that covers each source.
This fact can be exploited in order to save some computational memory.
Instead of storing all of the multiple $\mathbf{c}_k$ vectors
(Eq.~\ref{eq:gb-linear-model}), we can initialize a single $\mathbf{c}$ vector
full of zeros, where each element represents the coefficient of each one of the
original $M$ sources.
After each iteration of the gradient-boosting algorithm, we add the product of
the resulting coefficients $\hat{\mathbf{c}}_k$ and the step-size coefficient
$\alpha_k$  to the $\mathbf{c}$ vector, respecting the order of its elements.
Because the relation between the source coefficients and the effect they
generate is linear, we can safely compute the resulting field through
Equation~\ref{eq:eql-forward}.
This way the memory needed to store the entire set of estimated coefficients is
limited to a single vector of $M$ elements.
